Cooperative Control for Narrow Passage Traversal with an Ornithopter Micro Air Vehicle and Lightweight Ground Station

### 2012-10-10 manuscript.tex
Minor edits, update TODOs

% In the original styles from ACM, you would have needed to
% add meta-info here. This is not necessary for AAMAS 2013  as
% the complete copyright information is generated by the cls-files.

\title{Cooperative Control for Narrow Passage Traversal with an 
Ornithopter Micro Air Vehicle and Lightweight Ground Station}

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)
The flying platform used in this experiment is the H$^2$Bird flapping wing 
MAV. Built around the Silverlit I-Bird RC flyer powertrain and clap-fling 
wings, the H$^2$Bird has a wingspan of [40?] cm and weighs [14?] grams 
fully loaded. A tail propeller and servo-controlled tail elevator provide 
control in the yaw and pitch axes. An onboard electronics package combines 
a 40 MIPS microprocessor, 6 DOF IMU, 802.15.4 radio, VGA camera, and motor 
drivers with a 90 mAh lithium polymer battery for autonomous flight. In 
routine flight, the H$^2$Bird averages [insert speed] m/s ground speed and 
can operate for approximately [10] minutes.

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
%TODO(ryan)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}
%TODO(ryan)

@@

%----------------------------------------------------------------------------%
\subsection{Ornithoper Flight Control}
%TODO(humphrey)

\begin{figure}[tb]
\centering
%\includegraphics[width=\linewidth]{figures/h2bird_axes.png}
\includegraphics[height=150pt]{figures/h2bird_axes.png}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}

@@

Given a reference pose $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
linearize the error quaternion to produce body axis angular errors as as 
inputs to the attitude controllers.

@@

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO(ryan)

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO(ryan)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO(ryan)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO(cameron)

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
\label{sec:flight_control}
%TODO(cameron)
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO(cameron)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO(ryan)

>>>>

% In the original styles from ACM, you would have needed to
% add meta-info here. This is not necessary for AAMAS 2013  as
% the complete copyright information is generated by the cls-files.
\title{Cooperative Control for Narrow Passage Traversal with an 
Ornithopter Micro Air Vehicle and Lightweight Ground Station}

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
%TODO(humphrey)
The flying platform used in this experiment is the H$^2$Bird flapping wing 
MAV. Built around the Silverlit I-Bird RC flyer power train and clap-fling 
wings, the H$^2$Bird has a wingspan of [40?] cm and has a flight weight of 
13 grams. A tail propeller and servo-controlled tail elevator provide 
control in the yaw and pitch axes. An on-board electronics package comprises 
a 40 MIPS microprocessor, 6 DOF IMU, IEEE 802.15.4 radio, VGA camera, and motor 
drivers with a 90 mAh lithium polymer battery for autonomous flight. In 
routine flight, the H$^2$Bird averages [insert speed] m/s ground speed and 
can operate for approximately 10 minutes.

%TODO footnote for Silverlit I-Bird
%TODO measure wingspan
%TODO ground speed

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}
%TODO ryan

@@

%----------------------------------------------------------------------------%
\subsection{Ornithoper Flight Control}

\begin{figure}[tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.png}
\caption{H$^2$Bird Ornithopter with flight control axes}
\label{fig:h2Bird_axes}
\end{figure}

@@

Given a reference pose $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose. We then 
linearise the error quaternion to produce body axis angular errors as as 
inputs to the attitude controllers.

@@

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO ryan

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance}
%TODO cameron

%----------------------------------------------------------------------------%
\subsection{Ornithopter Flight Control}
\label{sec:flight_control}
%TODO cameron
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
%TODO ryan
